Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/related_work.tex
Update related_work.tex
edits

There are several lines of work related to finding a good network structure. We
describe them next:

@@

\noindent\textbf{Hyperparameter optimization techniques: }The most popular
techniques for hyperparameter optimization include simple methods such as random
search~\cite{BergstraJAMESBERGSTRA2012} which have been shown to work
suprisingly well compared to more complex methods such as those based on
Bayesian optimization~\cite{Snoek12}.  Brute force search of network sizes is
also become more practical due to faster and more powerful
hardware~\cite{molchanov2016pruning}.  The more complex methods for
hyperparameter optimization include techniques such as~\cite{Snoek12} which
model generalization performance via Gaussian Processes~\cite{GaussianProcesses}
and select hyperparameter combinations that come from uncertain areas of the
hyperparameter space. Recently, methods based on bandit algorithms (e.g.
~\cite{li2016hyperband, jamieson2016}) have also become a popular way to tune
hyperparameters. With respect to our work, these methods require many tens of
hundreds of models to be trained, which makes the process computationally
inefficient and slow. In contrast, with ShrinkNets all the hyperparameters
related to network size are reduced to a single parameter, as we explain next.
More importantly, none of the hyperparameter optimization methods focuses on
finding small networks, which is a crucial property of ShrinkNets, necessary to
achieve good inference times.

@@

\noindent\textbf{Model Compression: }Model compression techniques focus on
reducing the model size \emph{after} training, in contrast to ShrinkNets, which
reduces it \emph{while} training. 
Optimal brain damage~\cite{Cun} identifies connections in a network that are
unimportant and then prunes these connections.
DeepCompression~\cite{han2015deepcompression} takes this one step further and in
addition to pruning connections, it quantizes weights to make inference
extremely efficient.  A different vein of work such as ~\cite{romero2014fitnets,
hinton2015distilling} proposes techniques for distilling a network into a
simpler network or a different model. Because these techniques work after
training, they are orthogonal and complementary to ShrinkNets. 
%Unlike our technique which works during
%training, these techiques are used after training and it would be interesting to
%apply them to ShrinkNets as well. 
%\cite{Abadi2016b} share the common goal of
%removing entire blocks of parameter to maintain dense matrices, however their
%method only applies to convolutional layers.

\noindent\textbf{Auto-ML: }There is work that focuses on automatically learning
model architecture through the use of genetic algorithms and reinforcement
learning techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}. These
techniques are focused on learning higher-level architectures (e.g.,
building blocks for neural network architectures). In particular, they do not
focus on finding small but well-performing networks for inference, which is the
goal of ShrinkNets.

\noindent\textbf{Dynamically Sizing Networks: }The techniques closest to our
proposed method are those based on group sparsity such as
~\cite{Scardapane2017}, and those like~\cite{Philipp} who grow and shrink
dynamically the size of the network during training.  \cite{Scardapane2017}
presents a method that also deactivates neurons using a loss function based on
group-sparsity.  However, the exact details of how their method works are not
given, and their experimental results (on a small, fully connected network), are
substantially worse than ours as shown in Section~\ref{sec:experiments}.
~\cite{Philipp} propose a method called Adaptive Radial-Angular Gradient Descent
that adds neurons on the fly and removes neurons via an $l_2$ penalty.  However,
this approach requires a new optimizer and takes longer to converge compared to
ShrinkNets.

>>>>

There are several lines of work related to optimizing network structure.

@@

\noindent\textbf{Hyperparameter optimization techniques: }
One way to optimize network architecture is to use 
hyperparameter optimization.  Although many methods have been 
proposed, e.g., \cite{BergstraJAMESBERGSTRA2012,Snoek12},
randomized search has been shown to work surprising well.
%  Brute force search of network sizes is
%also become more practical due to faster and more powerful
%hardware~\cite{molchanov2016pruning}.  
The more complex methods for
hyperparameter optimization include techniques, e.g., ~\cite{Snoek12} typically
 select hyperparameter combinations that come from uncertain areas of the
hyperparameter space to search efficiency. 
As a generalization of this,  methods based on bandit algorithms (e.g.
~\cite{li2016hyperband, jamieson2016}) have also become a popular way to tune
hyperparameters by quickly discarding 
model configurations that perform badly. 
Although these methods could in theory be used to tune the number of neurons per layer
of a network, in practice no related work proposes this, because treating each layer as a hyperparameter
would lead an excessively large search space.
In contrast, with ShrinkNets the size of the network can be tuned with 
a single parameter, as we explain in the next section..
% More importantly, none of the hyperparameter optimization methods focuses on
% finding small networks, which is a crucial property of ShrinkNets, necessary to
% achieve good inference times.

@@

\noindent\textbf{Model Compression: }Model compression techniques focus on
reducing the model size \emph{after} training, in contrast to ShrinkNets, which
reduces it \emph{while} training. 
Optimal brain damage~\cite{Cun} identifies connections in a network that are
unimportant and then prunes these connections.
DeepCompression~\cite{han2015deepcompression} takes this one step further and in
addition to pruning connections, it quantizes weights to make inference
extremely efficient.  A different vein of work such as ~\cite{romero2014fitnets,
hinton2015distilling} proposes techniques for distilling a network into a
simpler network or a different model. Because these techniques work after
training, they are orthogonal and complementary to ShrinkNets. Further,
some of these techniques, e.g.,~\cite{Han2015,Cun}, produce sparse matrices that
are not likely to improve inference times even though they reduce network size.
%Unlike our technique which works during
%training, these techiques are used after training and it would be interesting to
%apply them to ShrinkNets as well. 
%\cite{Abadi2016b} share the common goal of
%removing entire blocks of parameter to maintain dense matrices, however their
%method only applies to convolutional layers.

\noindent\textbf{Auto-ML: } Some work that focuses on automatically learning
model architecture through the use of genetic algorithms and reinforcement
learning techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}. These
techniques are focused on learning higher-level architectures (e.g.,
building blocks for neural network architectures). In particular, they do not
focus on finding small but well-performing networks for inference, which is the
goal of ShrinkNets.

\noindent\textbf{Dynamically Sizing Networks: }The techniques closest to our
proposed method are those based on group sparsity such as
~\cite{Scardapane2017}, and those like~\cite{Philipp} that dynamically grow and shrink
 the size of the network during training.  \cite{Scardapane2017}
presents a method that also deactivates neurons using a loss function based on
group-sparsity.  However, the exact details of how their method works are not
given, and their experimental results (on a small, fully connected network), are
substantially worse than ours as shown in Section~\ref{sec:experiments}.
\cite{Philipp} propose a method called Adaptive Radial-Angular Gradient Descent
that adds neurons on the fly and removes neurons via an $l_2$ penalty.  However,
this approach requires a new optimizer and takes longer to converge compared to
ShrinkNets.
